Manuscript

### 2022-09-02 analysis/manuscript.Rmd
fix small typo
remove duplicate rows on `max_C_data`

                               #Phenotype == "Weight" & outcome_ID == "21002_irnt" ~ "Weight",
                               Phenotype == "Forced vital capacity (FVC), Best measure" ~ "FVC",
                               Phenotype == "Red blood cell (erythrocyte) count" ~ "RBC count",
                               Phenotype == "Place of birth in UK - north co-ordinate" ~ "Place of birth, NC",
                               TRUE ~ Phenotype)) %>%
  mutate(label_phenos = case_when(outcome_description %in% interesting_phenotypes ~ TRUE, TRUE ~ FALSE))

max_C_plot <- ggplot2::ggplot(data = max_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +

>>>>

                               #Phenotype == "Weight" & outcome_ID == "21002_irnt" ~ "Weight",
                               Phenotype == "Forced vital capacity (FVC), Best measure" ~ "FVC",
                               Phenotype == "Red blood cell (erythrocyte) count" ~ "RBC count",
                               Phenotype == "Place of birth in UK - north co-ordinate" ~ "Place of birth, NC",
                               TRUE ~ Phenotype)) %>%
  mutate(label_phenos = case_when(outcome_description %in% interesting_phenotypes ~ TRUE, TRUE ~ FALSE)) %>% 
  dplyr::select(Phenotype, label_phenos, same_trait_corr_minus_MR_est, corr_due_to_confounding_summ, 
                same_trait_corr_minus_MR_est_se, corr_due_to_confounding_summ_SE) %>% unique()

max_C_plot <- ggplot2::ggplot(data = max_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding_summ, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +
